The value of intermediation

### 2022-09-14 src/presentation/presentation.qmd
Include equilibrium entry graph in presentation

>>>>

::: {.r-stack}
::: {.fragment}
<video data-autoplay src="../../out/manim_figures/videos/equilibrium_entry/800p60/sections/draw_axes.mp4" />
:::
::: {.fragment}
<video data-autoplay src="../../out/manim_figures/videos/equilibrium_entry/800p60/sections/char_func.mp4" />
:::
::: {.fragment}
<video data-autoplay src="../../out/manim_figures/videos/equilibrium_entry/800p60/sections/fix_players.mp4" />
:::
::: {.fragment}
<video data-autoplay src="../../out/manim_figures/videos/equilibrium_entry/800p60/sections/P_profit_share.mp4" />
:::
::: {.fragment}
<video data-autoplay src="../../out/manim_figures/videos/equilibrium_entry/800p60/sections/profit_share_point.mp4" />
:::
::: {.fragment}
<video data-autoplay src="../../out/manim_figures/videos/equilibrium_entry/800p60/sections/hybrid_case.mp4" />
:::
::: {.fragment}
<video data-autoplay src="../../out/manim_figures/videos/equilibrium_entry/800p60/sections/switch_to_phi_F.mp4" />
:::
::: {.fragment}
<video data-autoplay src="../../out/manim_figures/videos/equilibrium_entry/800p60/sections/phi_F_functions.mp4" />
:::
::: {.fragment}
<video data-autoplay src="../../out/manim_figures/videos/equilibrium_entry/800p60/sections/cost_function.mp4" />
:::
::: {.fragment}
<video data-autoplay src="../../out/manim_figures/videos/equilibrium_entry/800p60/sections/equilibrium.mp4" />
:::
::: {.fragment}
<video data-autoplay src="../../out/manim_figures/videos/equilibrium_entry/800p60/sections/N_F_loss.mp4" />
:::
